---
title: PU5058 - Week Six - Practical Exercise
author: Victoria Avgoustis
date: November 19, 2023
output: pdf
---

# Aim
The aim of this exercise is to manipulate "Hip Replacement CCG 1819" data into a specific tidy data frame. 

# Load Packages
```{r Load Packages, include=FALSE}
library(tidyverse)
library(here)
library(ggplot2)
library(hrbrthemes)
```

# Read in Data

```{r Read Data}
operation_Data <- read_csv(here("01_Input/01_Raw-Data/Hip Replacement CCG 1819.csv"))
head(operation_Data)
```

# Prepare the Data
## Selecting Gender, Pre and Post Operation, and 'EQ-5D Index' scores
```{r Select Variables}
selected_Operation_Data <- operation_Data %>%
  select('Gender','Pre-Op Q EQ5D Index','Post-Op Q EQ5D Index') %>%
  rename(
    Gender = 'Gender',
    Pre_Op_Index = 'Pre-Op Q EQ5D Index',
    Post_op_Index = 'Post-Op Q EQ5D Index'
  )
glimpse(selected_Operation_Data)
```
## Check for Unique Vlues
```{r Unique}
selected_Operation_Data$Gender %>% unique()
selected_Operation_Data$Pre_Op_Index %>% unique()
selected_Operation_Data$Post_op_Index %>% unique()
```
## Check Value Frequencies
```{r Variable Frequency}
selected_Operation_Data$Gender %>% table()
selected_Operation_Data$Pre_Op_Index %>% table()
selected_Operation_Data$Post_op_Index %>% table()
```

## Remove Missing Values
```{r Remove Missing Values}
filtered_Operation_Data <- selected_Operation_Data %>%
  drop_na() %>%
  filter(Gender != '*')
glimpse(filtered_Operation_Data)
```
## Make Tidy Table
```{r Make Tidy}
tidy_Operational_Data <- filtered_Operation_Data %>%
  pivot_longer(c(Pre_Op_Index,Post_op_Index),
               names_to = 'Time',
               names_prefix = 'EQ5D_',
               values_to = 'EQ-5D Index'
               )
head(tidy_Operational_Data)
```
## Factors
```{r Factors}
tidy_Operational_Data$Time <- 
  factor(tidy_Operational_Data$Time,levels=c('Pre_Op_Index','Post_op_Index'))
tidy_Operational_Data
```
## Rename Index
```{r Rename Index}
plot_ready_Operational_Data <- tidy_Operational_Data %>%
  rename(EQ5D = 'EQ-5D Index')
plot_ready_Operational_Data
```

## Plotting
```{r}
fact_Operation_Data <- plot_ready_Operational_Data %>%
  mutate(Gender = factor(plot_ready_Operational_Data$Gender,levels=c('1','2')))

fact_Operation_Data %>%
  ggplot() +
  geom_boxplot(aes(x = Time, y = EQ5D, colour = Gender))

```


## Plotting... Muhahahah... Yes I know these graphs don't make much sense....

```{r Scatter Plot}

ggplot(fact_Operation_Data, aes(x=Gender,y=EQ5D,fill=Time)) + 
  geom_bar(stat = "identity", position = "identity") + 
  labs(title = "Simple Graphh",
       x="Gender",
       y="Time")
```
```{r Plotting}

x <- fact_Operation_Data$Gender
y <- fact_Operation_Data$Time
z <- fact_Operation_Data$EQ5D

ggplot(fact_Operation_Data, aes(x,y,fill=z)) + geom_tile()

```
## Part 2 - Calculate how many patients in this dataset have been told by a doctor that they have problems caused by a stroke
```{r}
stroke_table <- operation_Data %>%
  select(operation_Data$Stroke) %>%
  summarise(Stroke_total = sum(operation_Data$Stroke))
stroke_table
```
## Part 3 - Create a clean and tidy table with pre and post operation activity levels
```{r}
operation_Data
```


```{r}
activity_data <- operation_Data %>%
  select('Pre-Op Q Activity','Post-Op Q Activity') %>%
  pivot_longer(cols = c('Pre-Op Q Activity', 'Post-Op Q Activity'),
               names_to = 'Type',
               values_to = 'Activity')
activity_data

```


